### 2024-12-23 Notes/Notes.tex
Percentatge erased result

\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=1.5cm, bottom=3.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage[table,xcdraw]{xcolor}
\usepackage{enumitem}
\usepackage{float}
\usepackage{chemfig}
\usepackage{yfonts}
\usepackage{tikz}
\usepackage{forest}
\usepackage{wrapfig}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\useunder{\uline}{\ul}{}

@@

\begin{observation}
From Observation (\ref{observationCorrelationFactor}), one might hypothesize that training with chemical descriptors that have higher correlation factors, or discarding those with low correlation factors, would lead to better predictions. Numerically, however, this hypothesis is contradicted, as shown in Table (\ref{tableCorrelationFactorVariation}). Despite this, the result remains consistent with our core hypothesis: the correlation factor of a chemical descriptor does not necessarily indicate its relevance in protein inhibition. Our key assertion is that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}. \par

@@

\end{multicols}
\begin{table}[H]
\centering
\caption{Results for; Maximum $IC_{50}$ = 200 nM, Gap of the 25.0\% of the set, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training. The training is done with 200 trees.}
\label{tableCorrelationFactorVariation}
\begin{tabular}{c||c|c|c|c}
          &$\sigma\leq0$ & $\sigma\leq0.05$ & $\sigma\leq0.075$  & $\sigma\leq0.10$ \\\hline\hline
$r^2$ & 0.9607020297015885 & 0.9608545198149474 & 0.9605224652065423 & 0.9599158186858139 \\\hline
Mean Squared Error & 162.70220420738363 & 162.0708617391865 & 163.4456405456867 & 165.9572900112382 \\\hline
number of descriptors & 2911 & 1485 & 1001 & 568
\end{tabular}
\end{table}
\newpage

@@

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=1.5cm, bottom=3.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd, esint}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage[table,xcdraw]{xcolor}
\usepackage{enumitem}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{chemfig}
\usepackage{yfonts}
\usepackage{tikz}
\usepackage{forest}
\usepackage{pdflscape}
\usepackage{wrapfig}
\usepackage{url}
\usepackage[normalem]{ulem}
\usepackage{multicol}
\useunder{\uline}{\ul}{}

@@

\begin{observation}\label{ObsDescriptorsCorrelationFactor}
From Observation (\ref{observationCorrelationFactor}), one might hypothesize that training with chemical descriptors that have higher correlation factors, or discarding those with low correlation factors, would lead to better predictions. Numerically, however, this hypothesis is contradicted, as shown in Table (\ref{tableCorrelationFactorVariation}). Despite this, the result remains consistent with our core hypothesis: the correlation factor of a chemical descriptor does not necessarily indicate its relevance in protein inhibition. Our key assertion is that \emph{there exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}. \par

@@

\begin{observation}
The dependency on the gap generations seems much relevant than the dependency on the descriptors' correlation factor (Observation (\ref{ObsDescriptorsCorrelationFactor})). By changing the erased percentage (i.e. the fraction of data discarded in the gap generation) we can compute $r^2$ and the Mean Square Error (i.e. the statistical deviation) which provides the results depicted in Figure (\ref{FigPlotErasedPercentageVSRSquare}) and Figure (\ref{FigPlotErasedPercentageVSMeanSquaredError}) respectively.  
\end{observation}

\begin{figure}[H]
\caption{Plot of $\%_{\text{Erased}}$ vs $r^2$.For: maximum $IC_{50}$ = 200 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training. The training is done with 200 trees.}
\label{FigPlotErasedPercentageVSRSquare}
\begin{tikzpicture}
\begin{axis}[
    width=0.5\textwidth,
    height=8cm,
    xlabel={$\%_{\text{Erased}}$},
    ylabel={$r^2$},
    xmin=0, xmax=100,
    ymin=0.94, ymax=1.0,
    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
    ytick={0.9, 0.92, 0.94, 0.96, 0.98, 1.0},
    legend pos=south east,
    legend style={font=\small},
    tick label style={font=\small},
    label style={font=\small},
]

\addplot[
    color=magenta,
    mark=diamond*,
    thick
] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSRSquare.txt};

\end{axis}
\end{tikzpicture}
\end{figure}

\begin{figure}[H]
\caption{Plot of $\%_{\text{Erased}}$ vs $Mean Squared Error$.For: maximum $IC_{50}$ = 200 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training. The training is done with 200 trees.}
\label{FigPlotErasedPercentageVSMeanSquaredError}
\begin{tikzpicture}
\begin{axis}[
    width=0.5\textwidth,
    height=8cm,
    xlabel={$\%_{\text{Erased}}$},
    ylabel={Mean Squared Error},
    xmin=0, xmax=100,
    ymin=0, ymax=200,
    xtick={0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100},
    legend pos=north east,
    legend style={font=\small},
    tick label style={font=\small},
    label style={font=\small}
]

\addplot[
    color=magenta,
    mark=diamond*,
    thick
] table[x index=0, y index=1, col sep=space] {GeneralSources/ErasedPercentageVSMeanSquaredError.txt};

\legend{Mean Squared Error}
\end{axis}
\end{tikzpicture}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\begin{landscape}
\section{Results}
\begin{table}[H]
\centering
\caption{Results for; Maximum $IC_{50}$ = 200 nM, Gap of the 25.0\% of the set, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training. The training is done with 200 trees.}
\label{tableCorrelationFactorVariation}
\begin{tabular}{c||c|c|c|c}
          &$\sigma\leq0$ & $\sigma\leq0.05$ & $\sigma\leq0.075$  & $\sigma\leq0.10$ \\\hline\hline
$r^2$ & 0.9607020297015885 & 0.9608545198149474 & 0.9605224652065423 & 0.9599158186858139 \\\hline
Mean Squared Error & 162.70220420738363 & 162.0708617391865 & 163.4456405456867 & 165.9572900112382 \\\hline
number of descriptors & 2911 & 1485 & 1001 & 568
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Results for; Maximum $IC_{50}$ = 200 nM,  taking into account all the chemical descriptors, the 20.0\% of the remaining data is saved for testing and the  80.0\% for training. The training is done with 200 trees.}

\begin{tabular}{c||c|c|c|c}
$\%_{\text{Erased}}$  	& 0\% & 5\% & 10\%  & 15\% \\\hline\hline
$r^2$ 				& 0.9410691012016194 & 0.9450975181635125 & 0.9492662637374885 & 0.954840165823525 \\\hline
Mean Squared Error 		& 195.50415499282306 & 187.34588735050227 & 189.17427179281864 & 167.5904134577239 
\end{tabular}
\begin{tabular}{c||c|c|c|c} 
$\%_{\text{Erased}}$  	&  20\%  & 25\% & 30\% & 35\% \\\hline\hline
$r^2$ 				& 0.960093147530398 & 0.9607020297015885 & 0.9659474255238565 & 0.970950038525679 \\\hline
Mean Squared Error 		& 159.86610568752263 & 162.70220420738363 & 150.60605102824292 & 132.53106869928666
\end{tabular}
\begin{tabular}{c||c|c|c|c}
$\%_{\text{Erased}}$         & 40\%  & 45\% & 50\% & 55\% \\\hline\hline
$r^2$ 				& 0.9735150867866535 & 0.9761682347024537 & 0.9794766777874534 & 0.9836139552920377 \\\hline
Mean Squared Error 		& 130.3450775382814 &  124.45078192954777 & 112.31398471818515 & 94.8719409443141
\end{tabular}
\begin{tabular}{c||c|c|c|c}
$\%_{\text{Erased}}$  	&60\%  & 65\% & 70\% & 75\%  \\\hline\hline
$r^2$ 				&0.9858128266667714 & 0.9920845685273683 & 0.9950402754045806 & 0.9960292052079258\\\hline
Mean Squared Error 		&85.87640609411348 &  53.48552498895907 & 35.71100434005104 & 30.45304023300008
\end{tabular}

\begin{tabular}{c||c|c|c|c}
$\%_{\text{Erased}}$  	&80\%  & 85\% & 90\% & 95\% \\\hline\hline
$r^2$ 				&0.9971354719623441 & 0.9993589449322425 & 0.9996146336878613 & 0.9999982353685487\\\hline
Mean Squared Error 		&22.873087477997174 &  5.275980426255672 & 3.083365552988717 & 0.010325883398321972
\end{tabular}

\end{table}

\end{landscape}
